\normalfont\spacedallcaps{}

### 2019-02-13 Document/article_4.tex
logos2

\input{structure.tex}
\usepackage{adjustbox}
\usepackage{booktabs}
\hyphenation{Fortran hy-phen-ation} 
\captionsetup{font=footnotesize}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{tabularx, makecell}%
\renewcommand\theadfont{\normalsize\bfseries}
        \usepackage{etoolbox} %
        \AtBeginEnvironment{tabularx}{\setlist[enumerate, 1]{wide, leftmargin=*, itemsep=0pt, before=\vspace{-\dimexpr\baselineskip +2 \partopsep}, after=\vspace{-\baselineskip}}}

@@

Using phylogenetic trees of Trypanosoma in these works [][][][], we grouped TryTryp genomes as table \ref{table:4}. figure \ref{fig:countsclustered} shows a summery of the number of tRNA genes for each cluster and figure \ref{fig:funcclustered} shows the tRNA functional classes not annotated for clusters of genome. we excluded genome PconfusumCUL13 from the study, until we find a well sequenced version of this genome for which we can annotate all 22 functional classes of tRNAs. The Logo data for All TryTryp genomes and Human can be found here. 
In figure 8 you can see the bubble plots of each cluster in one page. in each page we have 22 models for each tRNA class. 
\begin{table}[hbt] 
\caption{Classification of TryTryp genomes. genomes not mentioned here are clustered as one genome.}
\begin{adjustbox}{width=\columnwidth,center}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
        \toprule LenriettiComplex & AfricanTrypanosome & AmericanTrypanosome & Leishmania1 & Leishmania2 &LDonovaniComplex & LMexicanaComplex & Lvianna \\\midrule
        \parbox{.45\textwidth} {\begin{enumerate}
            \item LspMARLEM2494
            \item LenriettiiLEM3045
        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
            \item TbruceigambienseDAL972
            \item TbruceiLister427
            \item TbruceiTREU927
            \item TevansiSTIB805
            \item TcongolenseIL3000
            \item TvivaxY486
        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
            \item TgrayiANR4
            \item TrangeliSC58
            \item TcruziCLBrener
            \item TcruziCLBrenerEsmeraldo-like
            \item TcruziCLBrenerNon-Esmeraldo-like
            \item TcruzicruziDm28c
            \item TcruziDm28c
            \item TcruziEsmeraldo
            \item TcruziJRcl4
            \item TcruzimarinkelleiB7
            \item TcruziSylvioX10-1
            \item TcruziSylvioX10-1-2012
            \item TcruziTulacl2
            \item TtheileriEdinburgh
        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
            \item CfasciculataCfCl
            \item LseymouriATCC30220
            \item LpyrrhocorisH10
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item LmajorFriedlin
            \item LmajorLV39c5
            \item LmajorSD75
            \item LturanicaLEM423
            \item LarabicaLEM1108
            \item LtropicaL590
            \item LaethiopicaL147
            \item LgerbilliLEM452
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item LdonovaniBHU1220
            \item LdonovaniBPK282A1
            \item LinfantumJPCM5
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item Lamazonensis\\
                  MHOMBR71973M2269
            \item Lmexicana\\MHOMGT2001U1103
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item Lbraziliensis\\MHOMBR75M2904
            \item Lbraziliensis\\MHOMBR75M2903
            \item Lpanamensis\\MHOMPA94PSC1
            \item Lpanamensis\\MHOMCOL81L13
        \end{enumerate}}\\
        \bottomrule
\end{tabular}
\label{table:4}
\end{adjustbox}
\end{table}

>>>>

\input{structure.tex}
\usepackage{cite}
\usepackage{adjustbox}
\usepackage{booktabs}
\hyphenation{Fortran hy-phen-ation} 
\captionsetup{font=footnotesize}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{tabularx, makecell}%
\renewcommand\theadfont{\normalsize\bfseries}
        \usepackage{etoolbox} %
        \AtBeginEnvironment{tabularx}{\setlist[enumerate, 1]{wide, leftmargin=*, itemsep=0pt, before=\vspace{-\dimexpr\baselineskip +2 \partopsep}, after=\vspace{-\baselineskip}}}

@@

Using phylogenetic trees of Trypanosoma from these works \cite{Souza:2018dg,Hughes:2003,Pothirat:2014,Kelly:2017}, we grouped TryTryp genomes as table \ref{table:4}. figure \ref{fig:countsclustered} shows a summery of the number of tRNA genes for each cluster and figure \ref{fig:funcclustered} shows the tRNA functional classes not annotated for clusters of genome. we excluded genome PconfusumCUL13 from the study, until we find a well sequenced version of this genome for which we can annotate all 22 functional classes of tRNAs. The Logo data for TryTryp genomes and Human can be found \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput/Logos}{here}. you can find the bubble plots for each cluster \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput/Logos/BubblePlots}{here}. we have 11 pages and each page has 21 models for all tRNA classes in a cluster. 
\begin{table}[hbt] 
\caption{Classification of TryTryp genomes. genomes not mentioned here are clustered as one genome.}
\begin{adjustbox}{width=\columnwidth,center}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
        \toprule LenriettiComplex & AfricanTrypanosome & AmericanTrypanosome & Leishmania1 & Leishmania2 &LDonovaniComplex & LMexicanaComplex & Lvianna \\\midrule
        \parbox{.45\textwidth} {\begin{enumerate}
            \item LspMARLEM2494
            \item LenriettiiLEM3045
        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
            \item TbruceigambienseDAL972
            \item TbruceiLister427
            \item TbruceiTREU927
            \item TevansiSTIB805
            \item TcongolenseIL3000
            \item TvivaxY486
        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
            \item TgrayiANR4
            \item TrangeliSC58
            \item TcruziCLBrener
            \item TcruziCLBrenerEsmeraldo-like
            \item TcruziCLBrenerNon-Esmeraldo-like
            \item TcruzicruziDm28c
            \item TcruziDm28c
            \item TcruziEsmeraldo
            \item TcruziJRcl4
            \item TcruzimarinkelleiB7
            \item TcruziSylvioX10-1
            \item TcruziSylvioX10-1-2012
            \item TcruziTulacl2
            \item TtheileriEdinburgh
        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
            \item CfasciculataCfCl
            \item LseymouriATCC30220
            \item LpyrrhocorisH10
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item LmajorFriedlin
            \item LmajorLV39c5
            \item LmajorSD75
            \item LturanicaLEM423
            \item LarabicaLEM1108
            \item LtropicaL590
            \item LaethiopicaL147
            \item LgerbilliLEM452
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item LdonovaniBHU1220
            \item LdonovaniBPK282A1
            \item LinfantumJPCM5
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item Lamazonensis\\
                  MHOMBR71973M2269
            \item Lmexicana\\MHOMGT2001U1103
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item Lbraziliensis\\MHOMBR75M2904
            \item Lbraziliensis\\MHOMBR75M2903
            \item Lpanamensis\\MHOMPA94PSC1
            \item Lpanamensis\\MHOMCOL81L13
        \end{enumerate}}\\
        \bottomrule
\end{tabular}
\label{table:4}
\end{adjustbox}
\end{table}
